Tutorial_3a

### 2024-10-21 Tutorial_3a.Rmd
rename 2 tuts
add fixed effects code

---
title: "Tutorial_3"
author: "Sven Panis"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "Tutorial_3a"
author: "Sven Panis"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

Fixed effects:

```{r effects-M3-f}
load("Tutorial_3_Frequentist/model_M3_f.RData")
fixef(model_M3_f)
```
